Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-09 tensor/draft/draft-tensor-op.tex
[tensor/draft] review content in sec. III and IV

With the first run of data taking by the LHCb Collaboration at the Large Hadron
Collider (LHC), $B$ physics has now also access to rather large samples of
rare $B$-meson decays with branching ratios below the $10^{-5}$. In consequence,
angular analyses of three- and four-body final states can be used to measure
a larger number of additional observables. Namely rare $B$ decays that are driven
at parton level by flavor-changing neutral current (FCNC) transitions $b\to s
\bar\ell\ell$ constitute valuable probes of the standard model (SM) and provide
constraints on its extensions, especially $B\to K^*(\to K\pi) \bar\ell\ell$, but
also $B\to K \bar\ell\ell$.

The angular distribution of $B\to K \bar\ell\ell$ in the angle $\theta_\ell$
between the $B$ and $\ell^-$ as measured in the dilepton rest frame
\begin{align}
  \label{eq:ang-distr}
  \frac{1}{\Gamma_\ell} \frac{\mbox{d}\Gamma_{\ell}}{\mbox{d}\!\cos\theta_\ell} &
  = \frac{3}{4} (1 - F_H^\ell) \sin^2\!\theta_\ell
  + \frac{1}{2} F_H^\ell
  + A_{\rm FB}^\ell \cos\theta_\ell \,,
\end{align}
normalised to the width $\Gamma_\ell$, has been recently updated with 3 fb$^{-1}$
by LHCb \cite{Aaij:2014tfa} for the mode $B^+\to K^+ \bar\mu\mu$, i.e. $\ell = \mu$,
with unprecedented precision, and the first analysis of $B^0\to K_{S} \bar\mu\mu$
has been reported as well. It provides the lepton-forward-backward asymmetry
$A_{\rm FB}^\mu$ and the flat term $F_H^\mu$ in CP-averaged form and integrated
over several bins in the dilepton invariant mass $q^2$. Similarly, the CP-averaged
branching ratios, ${\cal B}_\mu = \tau_{B} \Gamma_\mu$,~\cite{Aaij:2014pli}
and the rate CP asymmetry $A_{\rm CP}^\mu$ \cite{Aaij:2014bsa} are also
available from 3 fb$^{-1}$.

Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
factors for vector and dipole
couplings present in the SM, thereby enhancing their sensitivity to tensor and
scalar couplings \cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of
scalar couplings compared to helicity-suppressed vector couplings of the SM
is well-known from $B_s\to \bar\mu\mu$. Unfortunately the limited data set of
$B\to K^*(\to K\pi) \bar\ell\ell$ from LHCb \cite{Aaij:2013qta} still does not
allow to perform current angular analysis without the assumption of vanishing
scalar and tensor couplings in this decay mode. In the future also certain
angular observables in $B\to K^* \bar\ell\ell$ will provide additional constraints
on such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz}
and the linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
\cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the experimental
test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn}.

@@

This picture does not change in the presence of new physics contributions to
vector and dipole operators $i = 7,7',9,9',10,10'$. On the other hand,
non-vanishing tensor or scalar contributions are enhanced unless the
dynamics of NP implies similar suppression factors, i.e., lepton-Yukawa couplings
for $F_H^\ell$ or $\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular,
$F_H^\ell$ is very sensitive to tensor couplings whereas $A_{\rm FB}^\ell$ to
the interference of tensor and scalar couplings.

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
  %\includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \caption{ The sensitivity to the tensor coupling
      $\wilson{T}$ of $F_H$ [first row] and ${\cal B}$ [second row] in
      $B^+ \to K^+ \bar\mu\mu$ and ${\cal B}$ [third row], $J_{1c} +
      J_{2c}$ [fourth row], and $J_{1s}-3 J_{2s}$ [fifth row] in $B^0 \to K^{*0}
      \bar\mu\mu$ integrated over low- and high-$q^2$ bins. In the
      last two rows, the observables are normalized by the lifetime of
      the $B$ meson for easier comparison with the branching
      ratios. The bands represent the theory uncertainties at 68\%
      and 95\% probability.  For comparison, two sets of bands are
      shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
      $\wilson[NP]{9} = -1.1$ (red), and an additional band of the
      latest 68\% uncertainty reported by LHCb (grey) if a measurement
      is available.
      \todo{Perhaps restrict plots to range $C_T \in [-0.7, +0.7]$
            or even $\in [-0.5, +0.5]$?}}
  \label{fig:FHvsCT}
\end{figure*}

There are also angular observables $J_i$ in $B\to K^*(\to K\pi)\,
\bar\ell\ell$ with the same properties, i.e. tensor and scalar contributions
are kinematically enhanced by a factor $\sqrt{q^2}/m_\ell$ over vector ones
present in the SM or their respective interference terms. These are $J_{6c}$
and the two linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
with explicit formulas given in \refapp{app:BKstarellell}.
In the limit of vanishing lepton mass one obtains that
\begin{align}
  J_{6c} & \propto
    \mbox{Re}\big[(\wilson[]{P} - \wilson[]{P'})\, \wilson[\ast]{T}
                - (\wilson[]{S} - \wilson[]{S'})\, \wilson[\ast]{T5}\big]
\intertext{is sensitive to the interference of tensor and scalar operators,
  complementary to the $A_{\rm FB}^\ell$ in $B\to K \bar\ell\ell$}
  \label{eq:AFB-dependence}
  A_{\rm FB}^\ell & \propto
    \mbox{Re}\big[(\wilson[]{P} + \wilson[]{P'})\, \wilson[\ast]{T5}
                + (\wilson[]{S} + \wilson[]{S'})\, \wilson[\ast]{T}\big]
                \Big/ \Gamma_\ell \,,
\end{align}
i.e., with an interchange of tensor contributions $T \leftrightarrow T5$.
We note also that $J_{6c}$ contributes to lepton forward-backward asymmetry
of $B\to K^* \bar\ell\ell$ being $\propto (J_{6s} + J_{6c}/2)$. Since
it has to compete with $J_{6s}$ in this observable, a separate measurement of
$J_{6s}$ and $J_{6c}$ is necessary. Further, only tensor contributions enter
\begin{align}
  (J_{1s} - 3\, J_{2s}) & \propto
  \left(\ldots |\wilson{T}|^2 + \ldots |\wilson{T5}|^2 \right) \,,
\end{align}
where the dots indicate different kinematical and form factor dependences.
On the other hand, tensor and scalar contributions enter
\begin{equation}
\begin{aligned}
  (J_{1c} + J_{2c}) & \propto
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2 \right)
\\
  & + \ldots \left(|\wilson{S} - \wilson{S'}|^2 + |\wilson{P} - \wilson{P'}|^2 \right) \,,
\end{aligned}
\end{equation}
which is similar to the dependence of $F_H^\ell$ in $B\to K
\bar\ell\ell$
\begin{equation}
  \label{eq:FH-dependence}
\begin{aligned}
  F_H^\ell  \propto & \Big[
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2\right)
\\
  & + \ldots \left(|\wilson{S} + \wilson{S'}|^2 + |\wilson{P} + \wilson{P'}|^2 \right)
  \Big]
  \Big/ \Gamma_\ell \,.
\end{aligned}
\end{equation}
Concerning $F_H^\ell$, the involved kinematical factors --- see \cite{Bobeth:2007dw,
Bobeth:2012vn} --- are such that tensor and scalar couplings contribute only
constructively/cumulatively, apart of cancellations among $\wilson{S(P)}$ and $\wilson{S'(P')}$.
Further, interference terms (in the numerator of $F_H^\ell$) of $(\wilson{T} \times
\wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times \wilson{10,10'})$ are suppressed
by $m_\ell/\sqrt{q^2}$, but can become relevant in case that $\wilson{T} \ll \wilson{7,7',9,9'}$
and $\wilson{P,P'} \ll\wilson{10,10'}$ can overcome this suppression factor,
respectively.

@@

To illustrate the sensitivity of $F_H^\ell$ to tensor couplings, we compare
it in \reffig{fig:FHvsCT} to the one of the branching ratios of $B\to K^{(*)}
\bar\ell\ell$ \todo{$\ell = \mu$}, integrated over low and high $q^2$. The details of the numerical
input and the treatment of uncertainty propagation can be found in \refapp{app:theory:inputs}.
In view of the hint of new physics in $\wilson[NP]{9} < 0$ from recent global analysis of
$b\to s (\gamma,\, \bar\ell\ell)$ data \cite{Descotes-Genon:2013wba, Altmannshofer:2013foa,
Beaujean:2013soa, Hurth:2014vma, Altmannshofer:2014rta} we show besides
$\wilson[NP]{9} = 0$ also predictions for $\wilson[NP]{9} = -1.3$. As can be seen,
the sensitivity to tensor couplings is highest for $F_H^\ell$ at high $q^2$,
also due to a partial cancellation of form factors \cite{Bobeth:2012vn},
whereas the one on $\wilson[NP]{9} < 0$ is rather mild, in contrast to that of
the branching ratios. For the latter, ${\cal B}(B\to K^* \bar\ell\ell)$ shows
stronger dependence on $\wilson{T}$ compared to ${\cal B}(B\to K \bar\ell\ell)$
and has some impact on the constraints on tensor couplings as will be
discussed in \refsec{sec:results}. In consequence, the data on $F_H^\ell$ at
high $q^2$ provides currently the most stringent constraints on the size of
tensor couplings. Moreover, the dependence on vector couplings is such that
$\wilson[NP]{9} < 0$ leads to stronger constraints on $\wilson{T}$ than
$\wilson[NP]{9} \approx 0$.

Important additional constraints on scalar couplings come from the branching
ratio of $B_s \to \bar\mu\mu$ as given in \refeq{eq:Br-Bsmumu}. It provides
the most stringent constraints on the moduli $|\wilson{S} - \wilson{S'}|$
and $|\wilson{P} - \wilson{P'}|$ that are complementary to \refeq{eq:FH-dependence}
in $B\to K \bar\ell\ell$ and depends only on the further combination
$(\wilson{10} - \wilson{10'})$.

Eventually we also explore the behaviour of derived constraints with respect to
destructive interference with vector couplings $\wilson{9,\,9',\,10,\,10'}$.
For this purpose we include also the branching ratio, the lepton forward-backward
asymmetry and the rate CP asymmetry of $B\to K^* \bar\mu\mu$ as they provide
additional constraints on the real and imaginary parts of vector couplings.

In our fit of the effective couplings $\wilson{i}(\mu_b)$, we do not neglect
kinematically suppressed terms in predictions of measured observables as well
as when predicting not yet measured observables. The experimental input of these
observables is listed in \reftab{tab:observables} together with input for the
$B\to K^{(*)}$ form factors. More details on the latter can be found in
\refapp{app:theory:inputs}.

@@

In a scenario with only tensor complex-valued couplings $\wilson{T,\, T5}$,
the experimental measurement of $F_H^\mu$ constrains the combination
$|\wilson{T}|^2 + |\wilson{T5}|^2$, up to some small interference of
$\wilson{T}$ with vector couplings $\wilson{7,\,7',\,9,\,9'}$.
The according 68\% (95\%) 1D-marginalized probability intervals are listed in
\reftab{tab:cTT5:1-dimCLs}. As can be seen further in \reftab{tab:cTT5:1-dimCLs},
the constraints become tighter when utilising all observables in
\reftab{tab:observables}, mainly due to the sensitivity of the branching ratio of $B\to K^{*}
\bar\mu\mu$ to tensor couplings (see also \reffig{fig:FHvsCT}). The latter
stronger bounds are driven by the new lattice
results of $B\to K^*$ form factors that yield too high predictions compared
to the measurements~\cite{Horgan:2013pva}. Since tensor couplings contribute
constructively to ${\cal B}(B\to K^{*}\bar\mu\mu)$ large values are stronger
constrained. In this scenario, the measurements of $A_{\rm FB}^\mu(B^+\to K^+\bar\mu\mu)$
does not pose constraints due to vanishing scalar couplings.

Eventually, we perform a fit with non-zero complex-valued $\wilson{9,\,10}$
by allowing uniform priors for $\mbox{Re, Im}(\wilson{i}) \in[-7,\, 7]$,
($i = 9,10$) in order to access the stability of the bounds
against destructive interference. In this case, $F_H^\mu$ by itself still provides
bounds on $|\wilson{T,\,T5}|$ that are
weakened by a factor of two since $F_H^\mu$ does not pose constraints on
$\wilson{9,\,10}$ (in the chosen prior range). Once additional experimental
measurements of \reftab{tab:observables}
are taken into account, the potential destructive effects of new physics
in $\wilson{9,\,10}$ become reduced and almost the same constraints on $\wilson{T,\,T5}$
are recovered, as shown in \reftab{tab:cTT5:1-dimCLs}.
In consequence, the $F_H^\mu$ measurement~\cite{Aaij:2014tfa} of LHCb with
3 fb$^{-1}$ improves the previous bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$
by a \eos{factor of two}.

@@

Scalar couplings $\wilson{S,\, S',\, P,\, P'}$ enter $F_H^\ell$ without
kinematic suppression --- see \refeq{eq:FH-dependence} --- in the complementary
manner $(\wilson{i} + \wilson{i'})$ to the branching ratio
$\overline{\cal B}(B_s\to \bar\ell\ell)$, which constrains only $(\wilson{i} - \wilson{i'})$,
where $i = S,\, P$.
Most notably, we find that the current measurement of $F_H^\mu$ does constrain
the orthogonal $(\wilson{i} + \wilson{i'})$, such that the combination of $F_H^\mu$ and
$\overline{\cal B}(B_s \to \bar\mu\mu)$ allows to bound for the first time the moduli of
all four couplings.

The according four-parameter fit for complex-valued scalar couplings to the data of
$\overline{\cal B}(B_s \to \bar\mu\mu)$ and $F_H^\mu$ results in the (2D-marginalized)
regions in the $\mbox{Re}(\wilson{i} \pm \wilson{i'})$ ($i = S, P$)  planes shown in
\reffig{fig:scalar} and similarly for $\mbox{Im}(\wilson{i} \pm \wilson{i'})$. These
bounds do not change when including all other data in \reftab{tab:observables}, since
the $A_{\rm FB}^\mu(B\to K\bar\mu\mu)$ requires interference of scalar with tensor
couplings and other observables are not very sensitive to scalar
couplings. Quantitatively, the constraint from $\overline{\cal B}
(B_s \to \bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about \eos{a factor four to five}
stronger than the one of $F_H^\mu$ on $(\wilson{i} + \wilson{i'})$.

>>>>

With the analysis of the data collected by the LHCb Collaboration
during phase I at the Large Hadron Collider (LHC), we now have access
to rather large samples of rare $B$ meson decays with branching ratios
below $10^{-5}$. As a consequence, angular analyses of three- and
four-body final states can be used to measure a larger number of
observables than previously possible at the B factories BaBar and
Belle. In this work we focus on rare $B$ decays driven at the parton
level by the flavor-changing neutral-current (FCNC) transition $b\to s
\bar\ell\ell$ that constitutes a valuable probe of the standard model
(SM) and provides constraints on its extensions.

The angular distribution of $B\to K \bar\ell\ell$---normalized to the
width $\Gamma_\ell$---in the angle $\theta_\ell$ between $B$ and
$\ell^-$ as measured in the dilepton rest frame is
\begin{align}
  \label{eq:ang-distr}
  \frac{1}{\Gamma_\ell} \frac{\mbox{d}\Gamma_{\ell}}{\mbox{d}\!\cos\theta_\ell} &
  = \frac{3}{4} (1 - F_H^\ell) \sin^2\!\theta_\ell
  + \frac{1}{2} F_H^\ell
  + A_{\rm FB}^\ell \cos\theta_\ell \,.
\end{align}
LHCb recently analyzed their 3 fb$^{-1}$ data set and measured the
angular distribution of the mode $B^+\to K^+ \bar\mu\mu$, i.e. $\ell =
\mu$~\cite{Aaij:2014tfa}, with unprecedented precision to provide the
lepton-forward-backward asymmetry $A_{\rm FB}^\mu$ and the flat term
$F_H^\mu$ in CP-averaged form and integrated over several bins in the
dilepton invariant mass $q^2$\fred{sent. too long}. Similarly, the
CP-averaged branching ratios, ${\cal B}_\mu = \tau_{B}
\Gamma_\mu$,~\cite{Aaij:2014pli} and the rate CP asymmetry $A_{\rm
  CP}^\mu$ \cite{Aaij:2014bsa} are also available from 3 fb$^{-1}$.

Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong
suppression factors for vector and dipole couplings present in the SM,
thereby enhancing their sensitivity to tensor and scalar couplings
\cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of scalar
couplings compared to helicity-suppressed vector couplings of the SM
is well-known from $B_s\to \bar\mu\mu$. \fred{Which model gives rise
  to tensor contributions?} Unfortunately the limited data set of
$B\to K^*(\to K\pi) \bar\ell\ell$ from LHCb \cite{Aaij:2013qta} still
does not allow to perform current angular analysis without the
assumption of vanishing scalar and tensor couplings in this decay
mode. In the future also certain angular observables in $B\to K^*
\bar\ell\ell$ will provide additional constraints on such couplings,
as for example $J_{6c}$ \cite{Altmannshofer:2008dz} and the linear
combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
\cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the
experimental test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 =
0$~\cite{Bobeth:2012vn}.

@@

This picture does not change in the presence of new physics
contributions to vector and dipole operators $i =
7,7',9,9',10,10'$. On the other hand, non-vanishing tensor or scalar
contributions are enhanced unless the dynamics of NP implies similar
suppression factors, i.e., lepton-Yukawa couplings for $F_H^\ell$ or
$\alpha_e$ in the case of $A_{\rm FB}^\ell$. In particular, $F_H^\ell$
is very sensitive to tensor couplings $A_{\rm FB}^\ell$ is sensitive
to the interference of tensor and scalar couplings.

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
  %\includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \caption{ The sensitivity to the tensor coupling
      $\wilson{T}$ of $F_H$ [first row] and ${\cal B}$ [second row] in
      $B^+ \to K^+ \bar\mu\mu$ and ${\cal B}$ [third row], $J_{1c} +
      J_{2c}$ [fourth row], and $J_{1s}-3 J_{2s}$ [fifth row] in $B^0 \to K^{*0}
      \bar\mu\mu$ integrated over low- and high-$q^2$ bins. In the
      last two rows, the observables are normalized by the lifetime of
      the $B$ meson for easier comparison with the branching
      ratios. The bands represent the theory uncertainties at 68\%
      and 95\% probability.  For comparison, two sets of bands are
      shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
      $\wilson[NP]{9} = -1.1$ (red), and an additional band of the
      latest 68\% uncertainty reported by LHCb (grey) if a measurement
      is available.
      }
  \label{fig:FHvsCT}
\end{figure*}

There are also angular observables $J_i$ in $B\to K^*(\to K\pi)\,
\bar\ell\ell$ with the same properties, i.e. tensor and scalar
contributions are kinematically enhanced by a factor
$\sqrt{q^2}/m_\ell$ over vector ones present in the SM or their
respective interference terms. These are $J_{6c}$ and the two linear
combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$ with
explicit formulas given in \refapp{app:BKstarellell}. In our fits and
predictions we include all kinematically suppressed terms. But for the
purpose of illustration, we now consider the analytical dependence for
vanishing lepton mass. In this limit,
\begin{align}
  J_{6c} & \propto
    \mbox{Re}\big[(\wilson[]{P} - \wilson[]{P'})\, \wilson[\ast]{T}
                - (\wilson[]{S} - \wilson[]{S'})\, \wilson[\ast]{T5}\big]
\intertext{is sensitive to the interference of tensor and scalar operators,
  complementary to the $A_{\rm FB}^\ell$ in $B\to K \bar\ell\ell$}
  \label{eq:AFB-dependence}
  A_{\rm FB}^\ell & \propto
    \mbox{Re}\big[(\wilson[]{P} + \wilson[]{P'})\, \wilson[\ast]{T5}
                + (\wilson[]{S} + \wilson[]{S'})\, \wilson[\ast]{T}\big]
                \Big/ \Gamma_\ell \,,
\end{align}
i.e., with an interchange of tensor contributions $T \leftrightarrow T5$.
We note also that $J_{6c}$ contributes to lepton forward-backward asymmetry
of $B\to K^* \bar\ell\ell$ being $\propto (J_{6s} + J_{6c}/2)$. Since
it has to compete with $J_{6s}$ in this observable, a separate measurement of
$J_{6s}$ and $J_{6c}$ is necessary. Further, only tensor contributions enter
\begin{align}
  (J_{1s} - 3\, J_{2s}) & \propto
  \left(\ldots |\wilson{T}|^2 + \ldots |\wilson{T5}|^2 \right) \,,
\end{align}
where the dots indicate different kinematical and form factor dependences.
On the other hand, tensor and scalar contributions enter
\begin{equation}
\begin{aligned}
  (J_{1c} + J_{2c}) & \propto
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2 \right)
\\
  & + \ldots \left(|\wilson{S} - \wilson{S'}|^2 + |\wilson{P} - \wilson{P'}|^2 \right) \,,
\end{aligned}
\end{equation}
which is similar to the dependence of $F_H^\ell$ in $B\to K
\bar\ell\ell$
\begin{equation}
  \label{eq:FH-dependence}
\begin{aligned}
  F_H^\ell  \propto & \Big[
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2\right)
\\
  & + \ldots \left(|\wilson{S} + \wilson{S'}|^2 + |\wilson{P} + \wilson{P'}|^2 \right)
  \Big]
  \Big/ \Gamma_\ell \,.
\end{aligned}
\end{equation}
Concerning $F_H^\ell$, the involved kinematical factors --- see \cite{Bobeth:2007dw,
Bobeth:2012vn} --- are such that tensor and scalar couplings contribute only
constructively/cumulatively, apart of cancellations among $\wilson{S(P)}$ and $\wilson{S'(P')}$.
Further, interference terms (in the numerator of $F_H^\ell$) of $(\wilson{T} \times
\wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times \wilson{10,10'})$ are suppressed
by $m_\ell/\sqrt{q^2}$, but can become relevant in case that $\wilson{T} \ll \wilson{7,7',9,9'}$
and $\wilson{P,P'} \ll\wilson{10,10'}$ can overcome this suppression factor,
respectively.

@@

To illustrate the sensitivity of $F_H^\ell$ to tensor couplings, we
compare it in \reffig{fig:FHvsCT} to the one of the branching ratios
of $B\to K^{(*)} \bar\ell\ell$ for {$\ell = \mu$}, integrated over low
and high $q^2$. The details of the numerical input and the treatment
of uncertainty propagation can be found in \refapp{app:theory:inputs}.
In view of the hint of new physics in $\wilson[NP]{9} < 0$ from recent
global analysis of $b\to s (\gamma,\, \bar\ell\ell)$ data
\cite{Descotes-Genon:2013wba, Altmannshofer:2013foa, Beaujean:2013soa,
  Hurth:2014vma, Altmannshofer:2014rta} we show besides
$\wilson[NP]{9} = 0$ also predictions for $\wilson[NP]{9} = -1.1$. As
can be seen, the sensitivity to tensor couplings is highest for
$F_H^\ell$ at high $q^2$, also due to a partial cancellation of form
factors \cite{Bobeth:2012vn}, whereas the one on $\wilson[NP]{9} < 0$
is rather mild, in contrast to that of the branching ratios. For the
latter, ${\cal B}(B\to K^* \bar\ell\ell)$ shows stronger dependence on
$\wilson{T}$ compared to ${\cal B}(B\to K \bar\ell\ell)$ and has some
impact on the constraints on tensor couplings as will be discussed in
\refsec{sec:results}. In consequence, the data on $F_H^\ell$ at high
$q^2$ provides currently the most stringent constraints on the size of
tensor couplings. Moreover, the dependence on vector couplings is such
that $\wilson[NP]{9} < 0$ leads to stronger constraints on
$\wilson{T}$ than $\wilson[NP]{9} \approx 0$. \fred{Stress that
  $J_{1c}+J_{2c}$ and $J_{1s}-3J_{2s}$ robust against changes in
  $\wilson{9}$ but sensitive to $\wilson{T}$. $F_H$ sensitive to
  $\wilson[NP]{9}$ only if $\wilson{T} \ne 0$. Mention prior predictive}

Important additional constraints on scalar couplings come from the
branching ratio of $B_s \to \bar\mu\mu$ as given in
\refeq{eq:Br-Bsmumu}. It provides the most stringent constraints on
the moduli $|\wilson{S} - \wilson{S'}|$ and $|\wilson{P} -
\wilson{P'}|$ and further depends only on $(\wilson{10} -
\wilson{10'})$. Thus it is complementary to $F_H^{\ell}$ in $B\to K
\bar\ell\ell$; see Eq. \refeq{eq:FH-dependence}.

Eventually we also explore the effect of interference with NP in the
vector couplings $\wilson{9,\,9',\,10,\,10'}$ on the bounds on tensor
and scalar couplings.  For this purpose we include also the branching
ratio, the lepton forward-backward asymmetry and the rate CP asymmetry
of $B\to K^* \bar\mu\mu$ as they provide additional constraints on the
real and imaginary parts of $\wilson{9,\,9',\,10,\,10'}$.

The experimental inputs of all observables entering our fits is listed
in \reftab{tab:observables} together with input for the $B\to K^{(*)}$
form factors. More details on the latter can be found in
\refapp{app:theory:inputs}.

@@

In a scenario with only tensor complex-valued couplings $\wilson{T,\,
  T5}$, the experimental measurement of $F_H^\mu$ constrains the
combination $|\wilson{T}|^2 + |\wilson{T5}|^2$, up to some small
interference of $\wilson{T}$ with vector couplings
$\wilson{7,\,7',\,9,\,9'}$.  The according 68\% (95\%) 1D-marginalized
probability intervals are listed in the first column of
\reftab{tab:cTT5:1-dimCLs}. As can be seen further in the second
column, the constraints become tighter when utilising all observables
in \reftab{tab:observables}, mainly due to the sensitivity of the
branching ratio of $B\to K^{*} \bar\mu\mu$ to tensor couplings (see
also \reffig{fig:FHvsCT}). The latter stronger bounds are driven by
the new lattice results of $B\to K^*$ form factors that yield too high
predictions compared to the measurements~\cite{Horgan:2013pva}. Since
tensor couplings contribute constructively to ${\cal B}(B\to
K^{*}\bar\mu\mu)$ large values are stronger constrained. In this
scenario with vanishing scalar couplings, current measurements of
$A_{\rm FB}^\mu(B^+\to K^+\bar\mu\mu)$ barely provide any constraint;
cf.~\refeq{eq:AFB-dependence}.

We also perform a fit with non-zero complex-valued $\wilson{9,\,10}$
by allowing uniform priors for $\mbox{Re, Im}(\wilson{i}) \in[-7,\,
7]$, ($i = 9,10$) in order to access the stability of the bounds
against interference. Note that $\wilson{7,7'}$ appears in linear
combinations with $\wilson{9,9'}$ such that its interference with
tensor and scalar couplings is captured implicitly by allowing new
physics in $\wilson{9,9'}$. Thus we fix $\wilson{7,7'}$ to the SM
value without loss of generality. In this case, $F_H^\mu$ by itself
still provides bounds on $|\wilson{T,\,T5}|$ that are weakened by a
factor of two since $F_H^\mu$ does not pose constraints on
$\wilson{9,\,10}$ (in the chosen prior range). Once additional
experimental measurements of \reftab{tab:observables} are taken into
account, the potential destructive effects of new physics in
$\wilson{9,\,10}$ become reduced and almost the same constraints on
$\wilson{T,\,T5}$ are recovered, as shown in the third column in
\reftab{tab:cTT5:1-dimCLs}.  In consequence, the $F_H^\mu$
measurement~\cite{Aaij:2014tfa} of LHCb with 3 fb$^{-1}$ shrinks the
previous bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ by 50\%.

\fred{comment on last row: SM in all cartesian intervals but not in polar!}

@@

Scalar couplings $\wilson{S,\, S',\, P,\, P'}$ enter $F_H^\ell$
without kinematic suppression --- see \refeq{eq:FH-dependence} --- in
the complementary manner $(\wilson{i} + \wilson{i'})$ to the branching
ratio $\overline{\cal B}(B_s\to \bar\ell\ell)$, which constrains only
$(\wilson{i} - \wilson{i'})$, where $i = S,\, P$.  Most notably, we
find that the current measurement of $F_H^\mu$ does constrain the
orthogonal $(\wilson{i} + \wilson{i'})$, such that the combination of
$F_H^\mu$ and $\overline{\cal B}(B_s \to \bar\mu\mu)$ allows to bound
for the first time the real and imaginary parts of all four couplings.

The according four-parameter fit for complex-valued scalar couplings
to the data of $\overline{\cal B}(B_s \to \bar\mu\mu)$ and $F_H^\mu$
results in the (2D-marginalized) regions in the $\mbox{Re}(\wilson{i}
\pm \wilson{i'})$ ($i = S, P$) planes shown in
\reffig{fig:scalar}. The corresponding plots for $\mbox{Im}(\wilson{i}
\pm \wilson{i'})$ are very similar to those shown and thus
omitted. These bounds do not change when including all other data in
\reftab{tab:observables}, since the $A_{\rm FB}^\mu(B\to K\bar\mu\mu)$
requires interference of scalar with tensor couplings and other
observables are not very sensitive to scalar
couplings. Quantitatively, the constraint from $\overline{\cal B} (B_s
\to \bar\mu\mu)$ on $(\wilson{i} - \wilson{i'})$ is about a factor
four to five stronger than the one of $F_H^\mu$ on $(\wilson{i} +
\wilson{i'})$.

Interference terms of $\wilson{P,\,P'}$ with vector couplings might
weaken these bounds. Most important for $\overline{\cal B}(B_s \to
\bar\mu\mu)$ are $(\wilson{10} - \wilson{10'})$ --- compare
\refeq{eq:Br-Bsmumu:time0} --- and for $F_H^\ell$ similarly
$(\wilson{10} + \wilson{10'})$ \cite{Bobeth:2007dw}, which are
suppressed by factors $m_\mu/M_{B_s}$ and $m_\mu/\sqrt{q^2}$,
respectively \fred{hard to read}. However, these terms become
important for small $\wilson{P,\,P'}$ due to the large SM contribution
of $\wilson[SM]{10} \simeq -4.2$. We compile bounds on complex-valued
scalar couplings in \reftab{tab:cSP:1-dimCLs} for only $F_H^\mu$, only
$\overline{\cal B}(B_s \to \bar\mu\mu)$, and their combination with
all the other observables in \reftab{tab:observables}. In the last
case, we allow new physics in vector couplings $\wilson{9,\ 9',\,
  10,\, 10'}$ assuming uniform priors for $\mbox{Re, Im}(\wilson{i})
\in[-7,\, 7]$.  Neither $F_H^\ell$ nor $\overline{\cal B}(B_s \to
\bar\ell\ell)$ alone can bound all four complex-valued scalar
couplings, however their combination is capable to do so and moreover,
the bounds are stable against destructive interference with vector
couplings. In the special case of real-valued couplings,
$\overline{\cal B}(B_s \to \bar\ell\ell)$ would lead to
rings~\cite{Alonso:2014csa} instead of circles. In the most general
scenario, we find the following bounds with 68\% (95\%) probability:
\begin{equation}
  \begin{aligned}
    \left| \wilson{S} \right| & \in [0.06,\, 0.25]\; ([0.01,\, 0.36]),\\
    \left| \wilson{S'} \right| & \in [0.09,\, 0.46]\; ([0.02,\, 0.73]),\\
    \left| \wilson{P} \right| & \in [0.05,\, 0.21]\; ([0.01,\, 0.32]),\\
    \left| \wilson{P'} \right| & \in [0.11,\, 0.42]\; ([0.02,\, 0.63]).
  \end{aligned}
\end{equation}

Our results improve and extend previous bounds in the literature to
the most general case of complex-valued couplings. For example they
are a factor two to five more stringent than \cite{Becirevic:2012fy}
and comparable to \cite{Altmannshofer:2012az} once restricting to the
much simpler scenarios considered there.
